### 2009-04-02 docs/eos_notes/eos_notes.tex
missed one case added flag logic

@@

@@

@@

of $\dt.$}\\
If {\tt use\_thermal\_diffusion} = T:

@@

If {\tt use\_thermal\_diffusion} = F:

@@

\item[Step 6.] {\em Define a new average expansion rate at time $t^\nph.$}

@@

@@

\item[Step 10.] {\em Compute $S^{n+1}$ for the final projection.}

@@

@@

\item[Step 6.] {\em Define a new average expansion rate at time $t^\nph.$}

@@

\item[Step 10.] {\em Compute $S^{n+1}$ for the final projection.}

>>>>

\item[Step 1.] {\em Define the average expansion at time $t^\nph$ and the new $w_0.$}\\ \\
if {\tt dpdt\_factor} $>$ 0 then

@@

end if

@@

if {\tt evolve\_base\_state} then

@@

of $\dt.$}\\ \\
if {\tt use\_thermal\_diffusion} = T then

@@

else

@@

end if
\item[Step 6.] {\em Define a new average expansion rate at time $t^\nph.$}\\ \\
if {\tt use\_thermal\_diffusion} then

@@

if {\tt dpdt\_factor} $>$ 0 then

@@

end if
\item[Step 10.] {\em Compute $S^{n+1}$ for the final projection.}\\ \\
if {\tt make\_explicit\_thermal} then

@@

\item[Step 11.] {\em Update the velocity.}\\ \\
if {\tt dpdt\_factor} $>$ 0 then
\item In {\tt makePfromRhoH}, we compute a thermodynamic $p^{n+1}$ for the volume 
discrepancy term using $(\rho,h,X)^{n+1}$.
end if

@@

\item[Step 6.] {\em Define a new average expansion rate at time $t^\nph.$}\\ \\
if {\tt use\_thermal\_diffusion} then

@@

\item[Step 10.] {\em Compute $S^{n+1}$ for the final projection.}\\ \\
if {\tt make\_explicit\_thermal} then
